Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-02 paper/paper.tex
motivation for gen alg

\paragraph{Genetic Optimization}
Genetic Optimization:

>>>>

\paragraph{Genetic Optimization}
Due to the stochastic nature of the fitness function $F_C(G)$ of a generator $G$, and the fact that single evaluations
of $F_C$ are computationally expensive, thus preventing increasing the number of samples such that the estimation $E(F_C)$
becomes sufficiently smooth, typical optimization methods like gradient descent or simulated annealing are not usable.

 On approach would be to use techniques from Monte Carlo Integration, e.g. stratified or importance sampling, to aid in the
evaluation of $E(F_C)$, but since $G(\lambda)$ depends noncontinuously on $\lambda$, it can only be applied to the dependence 
on the challenge $C$. This would mitigate the effects, but not solve the problem.

Therefore, we optimized using a genetic algorithm, which is inherently capable of coping with the stochastic fitness function.
